---
title: "Sampling Distributions Lab"
author: "Juliana Meirelles"
date: "Apr 21 2021"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(infer)
```

### Exercise 1

12 people out of the 50 people sampled believe that the work scientists do does not benefit them. 12/50 is 24% of the sample, whereas our population statistic for people who do not believe the work scientists do benefits them is 20%. In the sample, 76% of people do believe scientist's work benefits them, while in our population that number is 80%. 

```{r code-chunk-label}
global_monitor <- tibble(
  scientist_work = c(rep("Benefits", 80000), rep("Doesn't benefit", 20000))
)

samp1 <- global_monitor %>%
  sample_n(50)
```

### Exercise 2

I would expect my sample proportion to be slightly different than the sample proportion of another student's sample proportion if we do not set a seed, however, I believe they would be very close to each other in similarity because we are still working with the same sample size out of the same population.

```{r}
samp1 %>%
  count(scientist_work) %>%
  mutate(p_hat = n /sum(n))
```

### Exercise 3

The sample proportion of samp2 is different than that of samp1 because the percent of people who do not believe scientist's and their work benefit them is 12%, rather than samp1 which was 24%. The percent of believe who do believe they benefit from scientist's work is 88% in samp2, but only 76% in samp1. If we took two more samples of size 100 and size 1000, respectively, the sampleof 1000 would provide a more accurate estimate of the population proportion.

```{r}
samp2 <- global_monitor %>%
  sample_n(50)
```

### Exercise 4

HThere are 4 different elements (or variables) in sample_props50, and 15000 samples. The sampling distribution's center is around 0.2 p_hat, and spreads from about 0.02 p_hat to 0.05 p_hat. Describe the sampling distribution, and be sure to specifically note its center.

```{r}
sample_props50 <- global_monitor %>%
                    rep_sample_n(size = 50, reps = 15000, replace = TRUE) %>%
                    count(scientist_work) %>%
                    mutate(p_hat = n /sum(n)) %>%
                    filter(scientist_work == "Doesn't benefit")

ggplot(data = sample_props50, aes(x = p_hat)) +
  geom_histogram(binwidth = 0.02) +
  labs(
    x = "p_hat (Doesn't benefit)",
    title = "Sampling distribution of p_hat",
    subtitle = "Sample size = 50, Number of samples = 15000"
  )
```

### Exercise 5

There are 22 observations in this object called sample_props_small. Each observation represents a sampling statistics that make up the sampling distribution.

```{r}
sample_props_small <- global_monitor %>%
                    rep_sample_n(size = 10, reps = 25, replace = TRUE) %>%
                    count(scientist_work) %>%
                    mutate(p_hat = n /sum(n)) %>%
                    filter(scientist_work == "Doesn't benefit")
```

### Exercise 6

Each observation in the sampling distribution represents the number of sample statistics that have a p_hat of a certain amount. As you increase the sample size, the mean becomes more centered, but remains almost the same and the distributions move closer to that of a normal distribution. The standard error decreases. The values do not change if you increase the number of simulations.
...

