---
title: "Lab: The Normal Distribution"
author: "Juliana Meirelles"
date: "Apr 5 2021"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
head(fastfood)
```

### Exercise 1

The Mcdonalds distribution is centered more toward the left of the plot and has high-value outliers to the right. The center is around 250 calories of fat. The Dairy Queen distribution is centered more around 200-220 calories of fat. There are some outliers in this graph, but there is a shorter tail than in the Mcdonalds distribution. 

```{r code-chunk-label}
mcdonalds <- fastfood %>%
  filter(restaurant == "Mcdonalds")
dairy_queen <- fastfood %>%
  filter(restaurant == "Dairy Queen")

ggplot(data = mcdonalds, aes(x = cal_fat)) +
  geom_histogram(binwidth = 30)

ggplot(data = dairy_queen, aes(x = cal_fat)) + 
  geom_histogram(binwidth = 30)
```

### Exercise 2

```{r}
dqmean <- mean(dairy_queen$cal_fat)
dqsd   <- sd(dairy_queen$cal_fat)
```

### Exercise 3

### Exercise 4

### Exercise 5

### Exercise 6

### Exercise 7

### Exercise 8

### Exercise 9
...

